Meta-analysis Manuscript Wrangling

### 2021-07-17 shared analysis files /manuscript_datavis_22jun21.Rmd
savings edits

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_acclim_ES<-dat_acclim_ES %>% 
  filter (!is.na(yi)) %>%
  mutate(metric = case_when(resp_def %in% c("log CO2 production", 
                                            "maximal swimming speed", 
                                            "Maximum burst swim speed", 
                                            "Oxygen consumption", 
                                            "Performance breadth (Tbr)",
                                            "Time to heat knockdown",
                                            "Scope of thermal tolerance (CTmax - CTmin)",
                                            "RMR", 
                                            "Speed", "Thermal preference", 
                                            "Topt", "Tpref", 
                                            "Ucrit", "Umax") ~ "Pmax",
                            resp_def %in% c("CTmin", "LTmin") ~ "CTmin",
                            resp_def %in% c("CT max", "CTmax", "LTmax", "ULT50") ~ "CTmax",
                            resp_def %in% c("LDH activity", "CCO activity", 
                                            "CS activity") ~ "Biochemical"
                            ))
```

@@

## Acclimation with temperature modifiers
```{r, echo=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
summary(temp_acclimation_model)
```

## Acclimation with trait modifiers
```{r, echo=FALSE}
trait_acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
                                mods = ~exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_acclimation_model
```

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=normalized_acclim, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp +environment +metric, 
               random = ~1 |  study_id/response_id,
                 method="REML") 
acclimation_model
```

@@

## Non-linear averaging model with temperature modifiers
```{r, echo= FALSE}
temp_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
                                mods = ~flux_range * mean_temp_constant,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_full_var_model
```

## Non-linear averaging model with trait modifiers
```{r, echo = FALSE}
trait_full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_full_var_model
```

@@

full_var_model <-rma.mv(yi, vi, data=normalized_var, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size  +environment +org_level +metric, 
               random = ~1 | study_id/response_id,
                 method="REML") 
full_var_model

@@

```{r}
#Model selection 
AIC(temp_acclimation_model, trait_acclimation_model, acclimation_model, temp_full_var_model, trait_full_var_model, full_var_model)
```

@@

ggplot(normalized_var, aes(y=yi, fill=mean_temp_constant, x=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "flux range",
       y ="SMD",
       fill = "mean temp")+
  theme(legend.position="bottom")+ 
  facet_wrap(~mean_temp_constant)
```

>>>>

# Note in the above, you loose ~15% of data because of missing sample sizes and SEs reported, below these are removed for now
dat_acclim_ES<-dat_acclim_ES %>% 
  filter (!is.na(yi)) %>%
  mutate(metric = case_when(resp_def %in% c("log CO2 production", 
                                            "maximal swimming speed", 
                                            "Maximum burst swim speed", 
                                            "Oxygen consumption", 
                                            "Performance breadth (Tbr)",
                                            "Time to heat knockdown",
                                            "Scope of thermal tolerance (CTmax - CTmin)",
                                            "RMR", 
                                            "Speed", "Thermal preference", 
                                            "Topt", "Tpref", 
                                            "Ucrit", "Umax") ~ "Pmax",
                            resp_def %in% c("CTmin", "LTmin") ~ "CTmin",
                            resp_def %in% c("CT max", "CTmax", "LTmax", "ULT50") ~ "CTmax",
                            resp_def %in% c("LDH activity", "CCO activity", 
                                            "CS activity") ~ "Biochemical"
                            ))

count(dat_acclim_ES, metric)
```

@@

## Acclimation with temperature modifiers
```{r, echo=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / response_id,
                 method="ML") 
temp_acclimation_model
```

## Acclimation with trait modifiers
```{r, echo=FALSE}
trait_acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
                                mods = ~exp_age + size + org_level + exposure_temp + metric, 
               random = ~1 |  study_id/  response_id,
                 method="ML") 
trait_acclimation_model
```

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=normalized_acclim, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp +environment +metric, 
               random = ~1 |  study_id/response_id,
                 method="ML") 
acclimation_model
```

@@

## Non-linear averaging model with temperature modifiers
```{r, echo= FALSE}
temp_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
                                mods = ~flux_range * mean_temp_constant,
               random = ~1 | study_id / response_id,
                 method="ML") 
temp_full_var_model
```

## Non-linear averaging model with trait modifiers
```{r, echo = FALSE}
trait_full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~exp_age + size + org_level +metric +environment, 
               random = ~1 |  study_id/ response_id,
                 method="ML") 
trait_full_var_model
```

@@

full_var_model <-rma.mv(yi, vi, data=normalized_var, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size  +environment +org_level +metric, 
               random = ~1 | study_id/response_id,
                 method="ML") 
full_var_model

full_no_org <- rma.mv(yi, vi, data=normalized_var, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size  +environment +metric, 
               random = ~1 | study_id/response_id,
                 method="ML")

@@

```{r}
#Model selection 
AIC(temp_acclimation_model, trait_acclimation_model, acclimation_model)

AIC(temp_full_var_model, trait_full_var_model, full_var_model, full_no_org)

@@

ggplot(normalized_var, aes(y=yi, fill=mean_temp_constant, x=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "flux range",
       y ="SMD",
       fill = "mean temp")+
  theme(legend.position="bottom")+ 
  facet_wrap(~mean_temp_constant)

ggplot(normalized_var, aes(y=flux_range, fill=yi > 0, x=mean_temp_constant))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  #geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis(discrete =TRUE)+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "mean temp",
       y ="fllux_range",
       fill = "yi")+
  theme(legend.position="bottom")+
  geom_smooth(method=lm)

ggplot(normalized_var, aes(y=flux_range, fill=yi > 0, x=mean_temp_constant))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  #geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis(discrete =TRUE)+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "flux range",
       y ="SMD",
       fill = "mean temp")+
  theme(legend.position="bottom")+
  geom_smooth(method=lm)

ggplot(normalized_var, aes(y=yi, fill=mean_temp_constant, x=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=3, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  #geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  #geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "flux_range",
       y ="yi",
       fill = "mean temp")+
  theme(legend.position="bottom")+
  geom_smooth(method=lm)+
  facet_wrap(~mean_temp_constant)

ggplot(normalized_acclim, aes(y=yi, x=flux_range, fill=mean_temp_reared))+
  geom_jitter(alpha = 0.5, pch=21,size=3, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  #geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  #geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Acclimation and fluctuation range")+
  labs(x = "mean temp",
       y ="yi",
       fill = " flux range")+
  theme(legend.position="bottom")+
  geom_smooth(method=lm)+
  facet_wrap(~mean_temp_reared)
